Supervised Learning for Psychological Attention to High School Students

### 2020-11-17 article/article.tex
[ article ] working
[ article ] started appendix plots

\section{Results}\label{sec:res}
\subsection{Support Vector Machines}

@@

\subsection{Neural Networks}
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[1,2,3]$ network (worst).}
    \label{fig:NN-worst}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.9-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.9-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.9-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[2]$ network (2nd best).}
    \label{fig:NN-2best}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.9-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.9-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.9-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[3]$ network (best).}
    \label{fig:NN-best}
\end{figure*}

@@

>>>>

\section{Results}\label{sec:res}
For giving an idea of the dataset treated in this work (visualization), the data
was embedded into a 2-dimensional space using the T-student Stochastic
Neighborhood Embedding (TSNE) \href{https://github.com/lejon/TSne.jl}{in Julia}
\parencite{maaten2008}. In Fig. \ref{fig:emb_dat}, the embedded dataset is
presented.
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/embedded-data.pdf}
  \caption{Embedded dataset.}
  \label{fig:emb_dat}
\end{figure}

\subsection{Support Vector Machines}

@@

\subsection{Neural Networks}
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[1,2,3]$ network $\eta=0.9$
    (worst).}
    \label{fig:NN-worst}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.9-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.9-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.9-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[2]$ network with $\eta=0.9$
     (2nd best).}
    \label{fig:NN-2best}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.9-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.9-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.9-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[3]$ network with $\eta=0.9$
    (best).}
    \label{fig:NN-best}
\end{figure*}

@@

\appendices

\section{Results for Embedded Data}
This section presents the same results above presented but for the data
embedded with the TSNE algorithm prior to training.
\subsection{Support Vector Machines}

\subsection{Decision Tree}
\begin{figure}
    \includegraphics[width=\columnwidth]{figs/tree-emb-graph.pdf}
    \caption{Decision tree.}
    \label{fig:dte}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figs/tree-contour-0-1.pdf}
    \caption{Decision Tree contour with real labels (embedded data).}
    \label{fig:dte_cont}
\end{figure}

\subsection{Neural Networks}
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[2,3,3]$ network with $\eta=0.9$
    (worst).}
    \label{fig:NN-emb-worst}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network
    (2nd best).}
    \label{fig:NN-emb-2best}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[2]$ with $\eta=0.2$ network
    (best).}
    \label{fig:NN-emb-best}
\end{figure*}
